A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

% \begin{table}[]
%   \begin{tabular}{lllllll}
%   \caption{Performance of the new attack method. We can see SSIM increases.}
%           & \multicolumn{2}{l}{Untargeted Attack} & \multicolumn{2}{l}{Targeted Attack} & \multirow{2}{*}{SSIM x} & \multirow{2}{*}{SSIM z} \\
%           & AO                & SR                & AO               & SR               &                         &                         \\
%   method1 & 0.1747            & 0.1442            & 0.8448           & 0.8972           & 0.56                    & 0.79                    \\
%   method2 &                   &                   &                  &                  & 0.78                    & 0.79                   
%   \end{tabular}
% \end{table}

%%%% 问题 3.2 %%%%
\textit{2. The proposed method and offline training phase should be explained more clearly. For instance, the termination of offline training or offline optimization is missed affecting perturbation values.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing the the perturbation update process in offline training, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size, and clipping pixel values of intermediate results after each step to ensure that they are in an $\epsilon$-neighbourhood of the original image.  This leads to the Basic Iterative Method (BIM) introduced in \cite{kurakin2017adversarial}:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{true})),
    \end{gathered}
\end{equation}
%\uline{where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.}
\uline{The BIM can be easily made into an attacker for a specific desired target class, called the Iterative Target Class Method \cite{kurakin2017adversarial}:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{target})).
  \end{gathered}
  \label{equ:itcm}
\end{equation}

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT1016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.'' with}
``\uline{We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT2016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set. (see Table \ref{tab:dataset})'' with}
``\uline{We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

\textbf{We have mentioned the reinitialization of of VOT-toolkit in Section IV.A of the revised manuscript:}
\uline{Different from other datasets, the VOT dataset has a reinitialization module. When the tracker loses the target (i.e., the overlap is zero between the predicted result and the annotation), the tracker will be reinitialized with the ground truth.}

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
写response

\textit{Optimization}
\uline{Before introducing the proposed method, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size, and clipping pixel values of intermediate results after each step to ensure that they are in an $\epsilon$-neighbourhood of the original image.  This leads to the Basic Iterative Method (BIM) introduced in \cite{kurakin2017adversarial}:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{true})),
    \end{gathered}
\end{equation}
%\uline{where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.}
\uline{The BIM can be easily made into an attacker for a specific desired target class, called the Iterative Target Class Method \cite{kurakin2017adversarial}:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{target})).
  \end{gathered}
  \label{equ:itcm}
\end{equation}

@@

\textit{Evaluation Benchmarks} We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, \ie, OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, \uline{VOT2016} \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.
Generally speaking, OTB2015 is a typical tracking benchmark which is widely used for evaluation for several years. 
GOT-10k has the advantage of magnitudes wider coverage of object classes. 
LaSOT has much longer video sequences with an average duration of 84 seconds.
UAV123 is utilized for unmanned aerial vehicle (UAV) tracking comprising 123 sequences. 
OTB2015, GOT-10k, LaSOT and UAV123 all follow the One-Pass Evaluation (OPE) protocol and their evaluation methodologies are similar as the measurement is mostly based on the success and precision of the trackers over the test videos. For instance, they all measure the success based on the fraction of frames in a sequence where the intersection-over-union (IoU) overlap of the predicted and ground truth rectangles exceeds a given threshold, and then the trackers are ranked using the area-under-the-curve (AUC) criterion. Since the average of IoU overlaps (AO) over all the test video frames is recently proved to be equivalent to the AUC criterion, we thus denote the success measurement as AO in the following. Besides AO, a success rate (SR) metric is also directly used to measure the percentage of successfully tracked frames given a threshold as in GOT-10k. As for the precision, it encodes the proportion of frames for which the center of the predicted rectangle is within 20 pixels of the ground truth center. Since the precision metric is sensitive to the resolution of the images and the size of the bounding boxes, a metric of normalized precision over the size of the ground truth bounding box is proposed and the trackers are then ranked using the AUC for normalized precision between 0 and 0.5. 
%\uline{
VOT \cite{VOT2016,VOT2018,VOT2019} introduces a series of tracking competitions with up to 60 sequences in each of them, aiming to evaluate the performance of a tracker in a relatively short duration. 
Three metrics are used to evaluate the performance of a tracker: (1) accuracy, (2) robustness and (3) EAO (expected average overlap). The accuracy measures how well the bounding box predicted by the tracker overlaps with the ground truth bounding box. The robustness measures how many times the tracker loses the target (fails) during tracking. EAO combines accuracy and robustness to evaluate the overall performance of the tracker.
Characteristics of the above datasets are summarized in Table \ref{tab:dataset}.
%}

>>>>

\textit{Optimization}
\uline{Before introducing the perturbation update process in offline training, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size, and clipping pixel values of intermediate results after each step to ensure that they are in an $\epsilon$-neighbourhood of the original image.  This leads to the Basic Iterative Method (BIM) introduced in \cite{kurakin2017adversarial}:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{true})),
    \end{gathered}
\end{equation}
%\uline{where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.}
\uline{The BIM can be easily made into an attacker for a specific desired target class, called the Iterative Target Class Method \cite{kurakin2017adversarial}:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{target})).
  \end{gathered}
  \label{equ:itcm}
\end{equation}

@@

\textit{Evaluation Benchmarks} We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, \ie, OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, \uline{VOT2016} \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.
Generally speaking, OTB2015 is a typical tracking benchmark which is widely used for evaluation for several years. 
GOT-10k has the advantage of magnitudes wider coverage of object classes. 
LaSOT has much longer video sequences with an average duration of 84 seconds.
UAV123 is utilized for unmanned aerial vehicle (UAV) tracking comprising 123 sequences. 
OTB2015, GOT-10k, LaSOT and UAV123 all follow the One-Pass Evaluation (OPE) protocol and their evaluation methodologies are similar as the measurement is mostly based on the success and precision of the trackers over the test videos. For instance, they all measure the success based on the fraction of frames in a sequence where the intersection-over-union (IoU) overlap of the predicted and ground truth rectangles exceeds a given threshold, and then the trackers are ranked using the area-under-the-curve (AUC) criterion. Since the average of IoU overlaps (AO) over all the test video frames is recently proved to be equivalent to the AUC criterion, we thus denote the success measurement as AO in the following. Besides AO, a success rate (SR) metric is also directly used to measure the percentage of successfully tracked frames given a threshold as in GOT-10k. As for the precision, it encodes the proportion of frames for which the center of the predicted rectangle is within 20 pixels of the ground truth center. Since the precision metric is sensitive to the resolution of the images and the size of the bounding boxes, a metric of normalized precision over the size of the ground truth bounding box is proposed and the trackers are then ranked using the AUC for normalized precision between 0 and 0.5. 
%\uline{
VOT \cite{VOT2016,VOT2018,VOT2019} introduces a series of tracking competitions with up to 60 sequences in each of them, aiming to evaluate the performance of a tracker in a relatively short duration. 
\uline{Different from other datasets, the VOT dataset has a reinitialization module. When the tracker loses the target (i.e., the overlap is zero between the predicted result and the annotation), the tracker will be reinitialized with the ground truth.}
Three metrics are used to evaluate the performance of a tracker: (1) accuracy, (2) robustness and (3) EAO (expected average overlap). The accuracy measures how well the bounding box predicted by the tracker overlaps with the ground truth bounding box. The robustness measures how many times the tracker loses the target (fails) during tracking. EAO combines accuracy and robustness to evaluate the overall performance of the tracker.
Characteristics of the above datasets are summarized in Table \ref{tab:dataset}.
%}
